Title Goes Here

### 2023-10-30 paper/main.tex
prior work WIP :

[ computer proofs of MPC paper; (double-check malicions case...)
  l-obliv
  wysteria et al
  probabilistic separation logic]
\subsection{Verification of MPC}

[Computer-aided proofs for multiparty computation with active security](https://arxiv.org/pdf/1806.07197.pdf)

>>>>

Formal methods exist for verifying MPC protocols.
\cite{https://arxiv.org/pdf/1806.07197.pdf} % Computer-aided proofs for multiparty computation with active security
use EasyCrypt to show the security of GMW,
but their technique is only applicable to a protocol with efficiently invertible functionality. 
and
\cite{Wysteria} % https://www.ieee-security.org/TC/SP2014/papers/Wysteria_c_AProgrammingLanguageforGeneric,Mixed-ModeMultipartyComputations.pdf
give fine-grain integration of 
[ computer proofs of MPC paper; (double-check malicions case...)
  l-obliv
  wysteria et al
  probabilistic separation logic]
\subsection{Verification of MPC}
